HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-02 paper/main.tex
spelling of assesment

After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}).
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments})
document HUME's inter-annotator agreement and efficiency (time of annotation). 
We further empirically compare HUME with direct assesment of human adequacy ratings,
and conclude by discussing the differences with HMEANT (\secref{sec:hmeant_comp}).

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{Plots of HUME scores vs Direct Assesment scores which have been standardised for each crowdsourcing annotator. The regression is calculated using linear least squares.}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{TODO} has proposed a new method for collecting 
accuracy ratings. The idea is that collecting a large number of adequacy judgements along a 
scale of 0 to 100 allows us to apply statistical measures which make them reliable. 
It has been shown that mean  judgements correlate very strongly with each other. 
We followed~\cite{TODO} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romanian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results. 
We can see that HUME and Direct Assesment scores do correlate. 
We also removed unreliable crowdsourcing annotators
according to the method discussed in ~\cite{TODO}. The Pearsons correlation for en-de is 0.58 and for en-ro is 0.70 which shows that they two measures do correlate. This confirms that 
the HUME metric is consistent with previously published methods in human evaluation, even though these
two approaches are very different in their conception.
We argue that although annotating HUME requires more expertise and effort, 
the results are more valuable because a HUME evaluation can tell you what parts
of the source sentence have been retained. Direct assesment scores require a crowd, which is sometimes not available or reliable, and it returns a single number which gives little insight into the quality of
the translated sentence.

>>>>

After a brief review (\secref{sec:background}), we describe HUME in detail
(\secref{sec:hume}).
Our experiments with four language pairs: English to Czech, German, Polish and Romanian (\secref{sec:experiments})
document HUME's inter-annotator agreement and efficiency (time of annotation). 
We further empirically compare HUME with direct assessment of human adequacy ratings,
and conclude by discussing the differences with HMEANT (\secref{sec:hmeant_comp}).

@@

\begin{figure}[t]
\renewcommand{\tabcolsep}{0pt}
\begin{tabular}{c}
\subfloat[English-German]{
  \iaafig{de}
}
\\
\subfloat[English-Romanian]{
  \iaafig{ro}
}
\end{tabular}
\caption{Plots of HUME scores vs Direct Assessment scores which have been standardised for each crowdsourcing annotator. The regression is calculated using linear least squares.}
\label{fig:dacorrelation}
\end{figure}
Recent research~\cite{TODO} has proposed a new method for collecting 
accuracy ratings. The idea is that collecting a large number of adequacy judgements along a 
scale of 0 to 100 allows us to apply statistical measures which make them reliable. 
It has been shown that mean  judgements correlate very strongly with each other. 
We followed~\cite{TODO} and collected up to 15 adequacy judgements on most of the
HUME annotated translations for German and Romanian. To ensure high quality judgments
we restricted the IP of the annotators to those of the relevant country. We found that there were too
few Czech and Polish annotators, and removing the IP restriction led to very poor quality results. 
We can see that HUME and Direct Assessment scores do correlate. 
We also removed unreliable crowdsourcing annotators
according to the method discussed in ~\cite{TODO}. The Pearsons correlation for en-de is 0.58 and for en-ro is 0.70 which shows that they two measures do correlate. This confirms that 
the HUME metric is consistent with previously published methods in human evaluation, even though these
two approaches are very different in their conception.
We argue that although annotating HUME requires more expertise and effort, 
the results are more valuable because a HUME evaluation can tell you what parts
of the source sentence have been retained. Direct assessment scores require a crowd, which is sometimes not available or reliable, and it returns a single number which gives little insight into the quality of
the translated sentence.
